RNAseq cia5 results

### 2024-04-23 2_B_dive_cia5/2_dive_cia5.Rmd
rename folder

@@

# 1. Load data
```{r load_data}
load(file=paste(dir,"dds_cia5.RDS", sep="/"))
load(paste(dir,"anno.RDS",sep="/"))

@@

# plap6
PLAP6 <- "Cre03.g188700"
d <- plotCounts(dds,gene = PLAP6, intgroup= c("treatment","genotype","condition"), returnData=TRUE)
g1 <- ggplot(d, aes(x = genotype, y = count, fill=genotype, color=genotype)) +
    geom_boxplot(color="black") +
    geom_point(shape=21,color="black",aes(fill=genotype),position=position_dodge(width=0.75), alpha=1) +
   scale_y_continuous(limits = c(60,150),trans = "log2") +
  scale_fill_manual(values = c("grey30","salmon")) + 
    labs(title = paste("PLAP6 (",PLAP6,")",sep=""))

# rbcl
anno[str_detect(anno[["Description"]],"RuBisCO"),1:9]
rbcl <- "CreCp.g802313"
d <- plotCounts(dds,gene = rbcl, intgroup= c("treatment","genotype","condition"), returnData=TRUE)
g2 <- ggplot(d, aes(x = genotype, y = count, fill=genotype, color=genotype)) +
    geom_boxplot(color="black") +
    geom_point(shape=21,color="black",aes(fill=genotype),position=position_dodge(width=0.75), alpha=1) +
   scale_y_continuous(trans = "log2") +
  scale_fill_manual(values = c("grey30","salmon")) + 
#  scale_color_manual(values = c("grey30","salmon")) + 
    labs(title = paste("rbcl (",rbcl,")",sep=""))
g1
g2
g1+g2 + plot_layout(guides = "collect", axes="collect", axis_titles="collect") & theme(legend.position = 'right')

>>>>

dir <- paste(s,"AG/AG-Scholz-NGS/Daten/Simon/P3043",sep="/")
gitdir <- paste(dir,"git_Chlamy_RNAseq_plap6",sep="/")
datadir <- paste(dir,"data",sep="/")
outdir <- gitdir
pubdir <- paste(s,"AG/AG-Scholz-NGS/Daten/Simon/P3043/git_Chlamy_RNAseq_plap6/pub_figures",sep="/")

@@

# 1. Load data
```{r load_data}
# load(paste(dir,"dds_cia5.RDS", sep="/"))
# load(paste(dir,"anno.RDS",sep="/"))

load("~/S/AG/AG-Scholz-NGS/Daten/Simon/Chlamy_RNASeq_aCRY/dds_cia5.RDS")
load("~/S/AG/AG-Scholz-NGS/Daten/Simon/Chlamy_RNASeq_aCRY/anno.RDS")

@@

# plap6
PLAP6 <- "Cre03.g188700"
d <- plotCounts(dds,gene = PLAP6, intgroup= c("treatment","genotype","condition"), returnData=TRUE)
g1 <- ggplot(d, aes(x = genotype, y = count, fill=genotype, color=genotype)) +
    geom_boxplot(color="black") +
    geom_point(shape=21,color="black",aes(fill=genotype),position=position_dodge(width=0.75), alpha=1) +
   scale_y_continuous(limits = c(60,150),trans = "log2") +
  scale_fill_manual(values = c("grey30","mediumpurple2")) + 
    labs(title = paste("PLAP6 (",PLAP6,")",sep=""))

# rbcl
anno[str_detect(anno[["Description"]],"RuBisCO"),1:9]
rbcl <- "CreCp.g802313"
d <- plotCounts(dds,gene = rbcl, intgroup= c("treatment","genotype","condition"), returnData=TRUE)
g2 <- ggplot(d, aes(x = genotype, y = count, fill=genotype, color=genotype)) +
    geom_boxplot(color="black") +
    geom_point(shape=21,color="black",aes(fill=genotype),position=position_dodge(width=0.75), alpha=1) +
   scale_y_continuous(trans = "log2") +
  scale_fill_manual(values = c("grey30","mediumpurple2")) + 
#  scale_color_manual(values = c("grey30","salmon")) + 
    labs(title = paste("rbcl (",rbcl,")",sep=""))
g1
g2
p <- g1+g2 + plot_layout(guides = "collect", axes="collect", axis_titles="collect") & theme(legend.position = 'right')

###### -export
```{r export_plap6, eval=FALSE}
ggexport(g1, filename = paste(pubdir,"Counts_cia5_PLAP6.pdf",sep="/"),width = 8.2, height = 4.7)
ggsave(g1, filename = paste(pubdir,"Counts_cia5_PLAP6.png",sep="/"),width = 8.2, height = 4.7)

ggexport(g2, filename = paste(pubdir,"Counts_cia5_rbcl.pdf",sep="/"),width = 8.2, height = 4.7)
ggsave(g2, filename = paste(pubdir,"Counts_cia5_rbcl.png",sep="/"),width = 8.2, height = 4.7)

ggexport(p, filename = paste(pubdir,"Counts_cia5_PLAP6+rbcl.pdf",sep="/"),width = 8.2, height = 4.7)
ggsave(p, filename = paste(pubdir,"Counts_cia5_PLAP6+rbcl.png",sep="/"),width = 8.2, height = 4.7)
